---
title: "Coding for Data Science Project: A shiny app to visualize VACCINATION CAMPAIGN"
author: "Andrea Pio Cutrera - 965591"
date: "4/9/2021"
output: pdf_document
---

## Shiny App for Vaccine

This is a shiny app that makes an easy visualization of the Vaccination Campaign in Italy. The APP scrapes data from the open repository of the Civil Protection Department of Italy <https://github.com/italia/covid19-opendata-vaccini>.

In the upper left part of the page, there is a side bar panel which allows to select the Region of interest and the particular Vaccine. Once selected, a plot of the distribution between the Age Range is given in output.

In order to run this app there are some requirements.
```R
library(shiny)
library(ggplot)
library(shinythemes)
```

This is an App <http://rmarkdown.rstudio.com>.


```R
shiny::runGitHub("shiny_app", "andreacutrera", ref="main")
```
You can embed an R code chunk like this:
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
